 

### 2020-05-12 docs/index.rmd
fix-index-github-activity

---
author: " "
bibliography:
- '../input/bib/zlibrary.bib'
csl:
- '../input/bib/apa6.csl'
title: " "
output:
    html_document:
      number_sections: false
---

>>>>

---
author: " "
bibliography:
- '../input/bib/zlibrary.bib'
csl:
- '../input/bib/apa6.csl'
title: " "
output:
    html_document:
        smart: false
        includes:
          in_header: head_github-activity.html
---
